\todo{TUM, Robert}

\begin{itemize}
	\item Selection of the meta-plugin
	The fixed-sequence plugin executes all the plugins from the sequence while the adaptive-sequence plugin execute only plugins from the sequence that satisfy the given criteria.
The adaptive-sequence plugin uses codified expert knowledge in the sense of performance properties to decide which plugins to run from the list of plugins requested.
Therefore, the fixed sequence plugin should be used when the user wants to squeeze the maximum performance possible by the non-cross-product approach. On the other hand, the adaptive-sequence should be used when the user wants to get the optimal combination of optimization parameters just for optimization aspects with the biggest potential.
The adaptive-sequence plugin should be used when we have limited time budget to get the optimum performance within that constraint. 


	\item The plugins whose tuning parameters do not interfere and whose tuning scenarios are not prepared in the same way are the perfect candidates for fixed or adaptive-sequence plugins.
The good candidates which can be combined with any other individual plugin are the CFS plugin and the DVFS plugin. For the fixed- and adaptive-sequence plugin we have used the CFS plugin, the DVFS plugin and the MPI parameters plugin. 

	\item Ordering of the plugin execution does not matter as they are executed sequentially.  
	
	\item Meta-plugins do not have any search strategies. Search strategy of the plugins executed by the meta-plugin is used.
\end{itemize}
