\subsubsection{Score-P developer tools}
Score-P developer tools used for Score-P development contain Libtool, Autoconf,
Automake, M4 macro system, uncrustify and doxygen.

Score-P developer tools are available as modules on some systems, like \textcolor{red}{SuperMUC or }
Taurus; or as source directly from a Score-P developers repository. Please note
that you need to be a Score-P developer to get credentials to Score-P
developers repository.

SuperMUC and Taurus already have modules for Score-P developer tools which can
be loaded by executing:

\texttt{module load scorep-dev}

To install them from source first clone the svn repository:

\texttt{svn co\\
\scorepdevurl\\
 scorep-dev}

Then, run the install script:

\texttt{sh install-scorep-dev.05.sh -{}-prefix=\installloc scorep-dev} \\

If you have installed Score-P developer tools under your home directory and not
system-wide you should specify its binaries location in the PATH environment
variable. To configure the location with bash shell execute the following
command:

\texttt{export PATH=\installloc scorep-dev:\$PATH}

\subsubsection{Lexer and parser generators: Bison v2.5+, LEX}
Lexer and parser generators are available on SuperMUC; as modules on some
systems, like Taurus; from Debian's APT and as source from the developers
webpage.

SuperMUC does not require Bison or LEX to be loaded as a module, it is
available by default.
Taurus already provides modules which can be loaded by executing:

\texttt{module load flex/2.5.39 bison/3.0.4}

In Debian-based distributions they are available as GNU Bison implementation of
YACC and flex through its apt-get package managements system. To install them
through Debian's APT execute the following command:

\texttt{sudo apt-get install bison flex}

To install them from source first download the packages, with aforementioned
version, and unpack them in a per-tool temporary directory. Then, run the
configure script:

\texttt{./configure -{}-prefix=\installloc <bison/flex>} \\

Then run:

\texttt{make}

When make has finished compiling the tool then install it by executing:

\texttt{make install}

Repeat the same procedure for the both tools.

If you have installed them under your home directory and not system-wide you
should specify its binaries location in the PATH environment variable. To
specify the location add the following command into your startup bash script,
i.e., \$HOME/.bashrc:

\texttt{export PATH=\installloc <bison/flex>/bin:\$PATH}


\subsubsection{Compilers: gcc, g++, gfortran, gcc-multilib}
SuperMUC already has compiler modules which can be loaded by executing:

\texttt{module load gcc/4.7}  (loads gcc, g++ and gfortran)

Taurus also has compiler modules which can be loaded by executing:

\texttt{module load gcc/4.6.2} (loads gcc, g++ and gfortran)

Compilers are available in many Linux distributions through its package management systems.
In Debian-based distributions it is available through its apt-get package managements system.

\texttt{sudo apt-get install gcc g++ gfortran gcc-multilib}

\subsection{Optional dependencies}

\subsubsection{(Optional) Documentation generation: Doxygen, LaTeX}

\paragraph{Doxygen} documentation generator

Doxygen package is available as a module on some systems, like SuperMUC and
Taurus; from a distribution package management system, like Debian's APT; or as
source directly from a tool developers webpage.

To install FLEX through Debian's APT execute the following command:

\texttt{sudo apt-get install doxygen}

SuperMUC already has doxygen module which can be loaded by executing:

\texttt{module load doxygen}

On Taurus doxygen is part of scorep-dev module.

To install from source first download it.
The location of source is:

\doxygenurl

Download and untar the tarball with the source.
Enter the directory where the source is located.

Configure the installation and specify the location where doxygen should be
installed.

\texttt{./configure --prefix=\installloc doxygen}

\texttt{make}

\texttt{make install}

If you have installed Doxygen under your home directory and not system-wide you
should specify its location in the PATH and LD\_LIBRARY\_PATH environment
variable. To specify the location add the following command into your startup
bash script, i.e., \$HOME/.bashrc:

\texttt{export PATH=\installloc doxygen/bin:\$PATH}

\paragraph{LaTeX} word processor

LaTeX package is available on Taurus; as a module on some systems; from a
distribution package management system, like Debian's APT; or as source directly
from a tool developers webpage.

To install FLEX through Debian's APT execute the following command:

\texttt{sudo apt-get install texlive-full}

